\documentclass[]{deedy-resume-openfont}
\usepackage{fontawesome}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Harikrishnan}{Rajan}{

\faEnvelopeO{\hspace{4pt} \href{mailto:hello@rhari.net}{hello@rhari.net}}
{\hspace{3pt} | \hspace{3pt} \faMobilePhone{\hspace{4pt} 9869089598}}
{\hspace{3pt} | \hspace{3pt} \faMapMarker{\hspace{4pt} Mumbai, India}}
\\ \vspace{4pt} \faGithub{\hspace{4pt}
\href{https://github.com/rhari991}{rhari991}}
{\hspace{3pt} | \hspace{3pt}
\faGlobe{\hspace{4pt}
\href{http://www.rhari.net}{rhari.net}}
{\hspace{3pt} | \hspace{3pt}
\faStackOverflow{\hspace{4pt} 
\href{https://stackoverflow.com/users/5762532/rhari}{rhari}}
{\hspace{3pt} | \hspace{3pt}
\faLinkedin{\hspace{4pt} 
\href{https://www.linkedin.com/in/rhari991/}{rhari991}}}}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{gobble}
\begin{minipage}[t]{0.48\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection {Google Summer of Code}
\descript{| Student developer }
\location{May 2017 – August 2017}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on the K-9 Mail application - an advanced email client for Android.
\item Optimized mail synchronization by adding support for the CONDSTORE and QRESYNC extensions for the IMAP protocol.
\item Refactored the server synchronization and push service code to be more modular and extendable.
\item Added support for the UID EXPUNGE command and MULTIAPPEND extension.
\end{tightemize}
\sectionsep

\runsubsection{Ride On Cab}
\descript{| Android development Intern }
\location{June 2016 – September 2016}
\begin{tightemize}
\item Worked on an Android application that lets it's users compare and book cabs across multiple providers.
\item Integrated the application with third-party APIs (Ola Cabs, Jugnoo Autos, MyTaxiIndia).
\item Routinely debugged both the Android application and the backend.
\end{tightemize}
\sectionsep

\runsubsection{Reliva Physiotherapy}
\descript{| Web Development Intern}
\location{June 2016}
\begin{tightemize}
\item Created an interactive calendar for appointment scheduling using Firebase, AngularJS and Bootstrap.
\end{tightemize}
\sectionsep

\runsubsection{Intellect Design Arena}
\descript{| Web Development Intern}
\location{December 2015 - January 2016}
\begin{tightemize}
\item Worked on a web application that demonstrated usage of the FusionCharts JavaScript library to implement several modern UI features.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 2000 lines:}
Java \textbullet{}   Android \\ 
\location{Over 500 lines:}
PHP \textbullet{} JavaScript \textbullet{} MySQL \textbullet{} Firebase \\
\location{Familiar:}
C \textbullet{} Python \textbullet{} CSS
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.48\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{PokeScanner}
\location{ \\An Android scanner for Pokemon Go.}
\vspace{\topsep}
\begin{tightemize}
\item Worked on an open-source application that lets users see the location of nearby Pokemon, catchable in Pokemon Go.
\item Worked on integrating the application with Google Maps and Location Services.
\item Added support for viewing and filtering Pokestops and Gyms.
\end{tightemize}
\sectionsep

\runsubsection{GoIV}
\location{ \\An IV calculator for Pokemon Go.}
\begin{tightemize}
\item Worked on an Android application that lets users prioritize which Pokemon to improve by calculating a special IV value for each Pokemon using optical character recognition.
\item Added on several features such as automatic updating, settings and crash reporting.
\end{tightemize}
\sectionsep

\runsubsection{PasteIO}
\location{ \\A Pastebin client for Android.}
\begin{tightemize}
\item Developed an application that lets users send, receive and share pieces of text with each other.
\item Built using a modern Android stack including RxJava, Realm and the MVP architecture pattern.
\end{tightemize}
\sectionsep

\runsubsection{Logistics Manager}
\location{ \\A pair of applications to manage delivery personnel.}
\begin{tightemize}
\item Created an Android application that shows it's user's real time position and relays it to a server.
\item Also developed a web application that lets it's user track the location of all field personnel and assign delivery jobs.
\item Used NodeJS and Socket.io for the server, as well as the Google Maps API for the maps on both applications.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Mumbai}
\descript{Bachelor of Engineering in Computer Science}
\location{VES Institute of Technology, Chembur
\\May 2013 - June 2017
\\CGPA - 7.75 (on a scale of 1 to 10)}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}